#load necessary tables
```{r}
library(XML)
library(rvest)
library(parallel)
library(plyr)
library(ggplot2)
```

### Taking a random sample of size of 50 pages of data from each UC.  Each page has 50 cases (except the last).

```{r}
campuses <- c("BERKELEY", "LOS+ANGELES", "SAN+DIEGO", "DAVIS", "IRVINE", "MERCED", "RIVERSIDE", "SAN+FRANCISCO", "UCOP", "SANTA+CRUZ", "SANTA+BARBARA")

names(campuses) <- campuses

campusURL <- function(campus){
  url1 <- "http://ucpay.globl.org/index.php?campus="
  url2 <- "&name=&title=&base=&overtime=&extra=&gross=%3E30000&year=&s=gross"
  paste(url1,campus,url2,sep="")
}

setSample <-function(campus,seed=1234){
  set.seed(seed)
  pages <- campusURL(campus) %>% htmlParse() %>% getNodeSet('//p[@class="pagelinks"]/a') %>% sapply(xmlValue)
  sample(as.numeric(pages[10]), floor(as.numeric(pages[10]) * 0.02))
}

samples<-lapply(campuses,setSample)
```

## Generates a List of Data Tables
```{r}
# Function that scrapes pages from UCPay
#http://ucpay.globl.org/index.php?campus=&name=&title=&base=&overtime=&extra=&gross=>30000&year=&s=gross
gettable <- function(pagenum,campus){
  tables<-read_html(paste(campusURL(campus),"&p=",pagenum, sep="")) %>% html_nodes(xpath="//table") %>% html_table(fill=TRUE)
  tables[[4]]
}  

UCtable <- function(campus,samples){
  # A random Sample
  randomPages <- samples[[campus]]
  lapply(randomPages,gettable,campus) %>% rbind.fill()
}

```

## Compute The List of Wage Data Frames from each UC campus in parallel
```{r}
UCtableList <- campuses %>%
  mclapply(UCtable,samples, mc.preschedule = FALSE)
```

##turn the UCtableList into a dataframe
```{r}
UCdataFrame<-rbind.fill(UCtableList) %>%
  mutate(`Base Pay`=as.numeric(gsub("[$,]","",`Base Pay`)),
     	`Overtime Pay`=as.numeric(gsub("[$,]","",`Overtime Pay`)),
     	`Extra Pay`=as.numeric(gsub("[$,]","",`Extra Pay`)),
     	`Gross Pay`=as.numeric(gsub("[$,]","",`Gross Pay`)))
```

###clean the table names by getting rid of commas and middle names
```{r}
UCdataFrame$Name <- UCdataFrame$Name %>% gsub(",","", .) %>% gsub("^([^ ]+) +([^ ]+).*", "\\2 \\1", .)
```

# Line Plots
```{r}
totalsalaries <- UCdataFrame %>%
      group_by(Year) %>%
      summarize(mean = mean(`Gross Pay`), mid = median(`Gross Pay`))

totalsalariesYearly <- UCdataFrame %>%
      group_by(Campus, Year) %>%
      summarize(mean = mean(`Gross Pay`), mid = median(`Gross Pay`))

#create a new theme
abluetheme <- theme(plot.background = element_rect(fill = "lightblue", colour = "black", size = 2, linetype = "solid"), legend.background=element_rect(colour = "black", size = 1, linetype = "solid"), panel.background=element_rect(colour = "black", size = 2, linetype = "solid"), plot.title=element_text(size=15))

#create average gross salary of UC campuses from 2004-2014
avglplot <- UCdataFrame %>%
  group_by(Year) %>%
  summarize(mean = mean(`Gross Pay`), mid = median(`Gross Pay`), SE = sd(`Gross Pay`)) %>%
  ggplot(aes(x=Year, y=mean)) + geom_line() + geom_point(size=2) + 
  geom_smooth(linetype=0, fill="light blue")+ geom_point(data=totalsalariesYearly, aes(x=Year, y=mean, col=Campus)) + 
  stat_summary() + 
  geom_line(data=totalsalariesYearly, aes(col=Campus, group=Campus)) + 
  labs(title="Average Gross Salary of UC Campuses, 2004-2014") + ylab("Mean Gross Pay") + scale_x_continuous(breaks=c(2004, 2006, 2008, 2010, 2012, 2014), labels=c(2004, 2006, 2008, 2010, 2012, 2014)) + 
  scale_y_continuous(labels = scales::dollar) +  
  abluetheme

#create average gross salary of UC campuses from 2004-2014 with standard errors
avglplot <- UCdataFrame %>%
  ggplot(aes(x=Year, y=`Gross Pay`))  +
  stat_summary(aes(group=Campus, col=Campus)) + 
  stat_summary(geom="line", aes(group=Campus, col=Campus)) + 
  stat_summary() + 
  stat_summary(geom="line") + 
  labs(title="Average Gross Salary of UC Campuses, 2004-2014") + ylab("Mean Gross Pay") + scale_x_continuous(breaks=c(2004, 2006, 2008, 2010, 2012, 2014), labels=c(2004, 2006, 2008, 2010, 2012, 2014)) + 
  scale_y_continuous(labels = scales::dollar) +  
  abluetheme

#create mean salary plot
avglplotYearly <- totalsalariesYearly %>% ggplot(aes(x=Year, y=mean)) + geom_line(aes(col=Campus, group=Campus)) + geom_point()  + labs(title="Mean Salary") + ylab("Mean") + abluetheme

#create median plot
midplot <- UCdataFrame %>%
  group_by(Year) %>%
  summarize(mean = mean(`Gross Pay`), mid = median(`Gross Pay`), SE = sd(`Gross Pay`)) %>%
  ggplot(aes(x=Year, y=mid)) + geom_line() + geom_point(size=2) + 
  geom_smooth(linetype=0, fill="light blue")+ geom_point(data=totalsalariesYearly, aes(x=Year, y=mid, col=Campus)) + 
  stat_summary() + 
  geom_line(data=totalsalariesYearly, aes(col=Campus, group=Campus)) + 
  labs(title="Median Salary of UC Campuses, 2004-2014") + ylab("Median Gross Pay") + scale_x_continuous(breaks=c(2004, 2006, 2008, 2010, 2012, 2014), labels=c(2004, 2006, 2008, 2010, 2012, 2014)) + 
  scale_y_continuous(labels = scales::dollar) +  
  abluetheme

```

# Stacked plot plot
```{r}
wideUCdataFrame <- UCdataFrame %>%
  gather(`Pay Type`, Amount, `Base Pay`, `Overtime Pay`, `Extra Pay`) %>%
  group_by(Campus, Year, `Pay Type`) %>%
  summarise(Amount = sum(Amount))

df <- wideUCdataFrame %>%
  ungroup() %>%
  unite(CampusPay, Campus, `Pay Type`, sep=" ")

stackedWide <- wideUCdataFrame  %>%
  filter(Campus=="BERKELEY") %>%
  ggplot(aes(x=Year, y=Amount, fill=`Pay Type`)) + geom_area(position = "stack") + 
  abluetheme + scale_y_continuous(labels = scales::dollar)

stackedPlotCampus <- df %>%
  ggplot(aes(x=Year, y=Amount, fill=CampusPay)) + geom_area(position = "stack") + abluetheme + scale_y_continuous(labels = scales::dollar)
```
#Profession wages between different universities 
```{r}
patternprof <- "PROF(?!ESSIONAL)|LECT"
patternpostgrad <- "POST"
patternhealth <- "(NURSE|CUSTODIAN|MECHANIC)"

searchPattern <- function(str){
      if (grepl(patternprof, str, perl=TRUE)) {
        return("Professor")
      } else if (grepl(patternpostgrad, str, perl=TRUE)) {
        return("Post Grad")
      } else if (grepl(patternhealth, str, perl=TRUE)) {
        return("Health")
      } else {
        return("Other")
      }
}

searchPatternVect <- function(vec) {
  return(sapply(X=vec, FUN=searchPattern))
}

UCLA_BerkDF <- UCdataFrame %>%
  filter(Campus=="LOS ANGELES" | Campus == "BERKELEY") %>%
  mutate(Title=searchPatternVect(Title))

BerkvsLA <- UCLA_BerkDF %>%
  group_by(Campus, Year, Title) %>%
  summarise(Average=mean(`Gross Pay`)) %>%
  ggplot(aes(x=Year, y=Average)) +
  geom_line(aes(col=Title)) +
  geom_point(aes(col=Title)) + 
  facet_wrap(~ Campus) + abluetheme +
  labs(title="Average Pay of Selected Profession: UC Berkeley vs. UCLA") + ylab("Mean Pay")

profAvglplot <- UCdataFrame %>% 
  mutate(Title=searchPatternVect(Title)) %>%
  group_by(Campus, Year, Title) %>%
  summarise(Average=mean(`Gross Pay`)) %>%
  ggplot(aes(x=Year, y=Average)) +
  geom_line(aes(col=Title)) +
  geom_point(aes(col=Title)) + 
  facet_wrap(~ Campus) + abluetheme +
  labs(title="Average Pay of Selected Profession, Faceted by Campus") + ylab("Mean Pay")

bigNames <- c("BERKELEY", "DAVIS", "IRVINE", "SAN DIEGO", "SAN FRANCISCO", "LOS ANGELES")

professionCountPlot1 <- UCdataFrame %>% 
  filter(Campus %in% bigNames) %>%
  mutate(Title=searchPatternVect(Title)) %>%
  ggplot(aes(x=factor(Year))) + geom_bar(aes(fill=Title)) + scale_x_discrete(breaks=c(2004, 2006, 2008, 2010, 2012, 2014), labels=c(2004, 2006, 2008, 2010, 2012, 2014)) + facet_wrap(~ Campus) + abluetheme + labs(title="Counts of each Profession Faceted by Campus") + ylab("Count") + xlab("Year")

professionCountPlot2 <- UCdataFrame %>% 
  filter(!(Campus %in% bigNames)) %>%
  mutate(Title=searchPatternVect(Title)) %>%
  ggplot(aes(x=factor(Year))) + geom_bar(aes(fill=Title)) + scale_x_discrete(breaks=c(2004, 2006, 2008, 2010, 2012, 2014), labels=c(2004, 2006, 2008, 2010, 2012, 2014)) + facet_wrap(~ Campus) + abluetheme + labs(title="Counts of each Profession Faceted by Campus") + ylab("Count") + xlab("Year")

professionCountTable <- UCdataFrame %>% 
  mutate(Title=searchPatternVect(Title)) %>%
  group_by(Campus, Title) %>%
  summarise(Total=n())

```

